---
title: "Week-5: Code-along"
author: "Lok"
date: "`r Sys.Date()`"
output:
  html_document:
  df_print: paged
pdf_document: default
---

  ```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# II. Code to edit and execute using the Code-along.Rmd file 
<br>

## A. Writing a function
<br>

### 1. Write a function to print a "Hello" message (Slide #14)

```{r, eval=TRUE,echo=TRUE}
say_hello_to <- function(name) {
  print(paste0("Hello", name,"!"))
}

```
<br>

### 2. Function call with different input names (Slide #15)

```{r, eval=TRUE,echo=TRUE}
say_hello_to('lok')
```
<br>

### 3. typeof primitive functions (Slide #16)

```{r, eval=TRUE,echo=TRUE}
typeof(sum)
```
<br>

### 4. typeof user-defined functions (Slide #17)

```{r, eval=TRUE,echo=TRUE}
typeof(say_hello_to)

```
<br>

### 5. Function to calculate mean of a sample (Slide #19)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean <- function(sample_size) {
  mean(rnorm(sample_size))
}
```
<br>

### 6. Test your function (Slide #22)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(1000)
```
<br>
```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(c(100,300,3000))
```
<br>

### 7. Customizing the function to suit input (Slide #23)

```{r, eval=FALSE,echo=TRUE}
library(tidyverse)
sample_tribble <- (sample_sizes = c(100,300,3000))

sample_tribble %>%
group_by(sample_sizes) %>%
mutate(sample_means = 
         calc_sample_mean(sample_sizes))
```
<br>

### 8. Setting defaults (Slide #25)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean <- function(sample_size,
                             our_mean=0,
                             our_sd=1) {
  sample <- rnorm(sample_size,
                  mean=our_mean,
                  sd=our_sd)
  mean(sample)
}

calc_sample_mean(sample_size = 10)
```
<br>

### 9. Different input combinations (Slide #26)

```{r, eval=TRUE,echo=TRUE}
calc_sample_mean(10,our_sd = 2)
calc_sample_mean(10,our_mean = 6)
calc_sample_mean(10,6,2)
```
<br>

### 10. Different input combinations (Slide #27)

```{r, eval=TRUE,echo=FALSE,error=FALSE} 
calc_sample_mean(10,our_mean = 5)
```
<br>

### 11. Some more examples (Slide #28)

```{r, eval=TRUE,echo=TRUE,error=FALSE} 
add_two <- function(x) {
  x+2
}
add_two(4)
add_two(-34)
add_two(5.654)
```
<br>

## B. Scoping
<br>

### 12. Multiple assignment of z (Slide #36)

```{r, eval=TRUE,echo=TRUE}
z <- 1
sprintf("the value assigned to z outside the funtion is %d",z)

foo <- function(z = 2) {
  z<-3
  return(z+3)
}
foo()
```
<br>

### 13. Multiple assignment of z (Slide #37)

```{r, eval=TRUE,echo=TRUE}
foo(z=4)
sprintf("the value assigned to z outside the funtion is %d",z)
```
<br>